### 2018-12-21 tex/paper.tex
Prelimiaries modified.

We can augment the above pairwise models with higher-order potentials. Let $\mathcal C$ be the set of cliques, which can, for instance, be the set of superpixels from an image segmentation method. Also, let $\bf x_c$ be the component of $\bf x$ formed by elements in clique $c$. The energy function now also contains higher-order potentials 
%
\begin{equation}
    E({\bf x}) = \sum_{a \in {\mathcal X}} \phi_a(x_a) + \sum_{(a, b) \in {\mathcal N}} \phi_{ab}(x_a, x_b) + \sum_{c \in {\mathcal C}} \phi_c({\bf x_c}),
    \label{eq:energy_hop_min}
  \end{equation}
%

@@

A higher-order model useful in real-world applications is the \textit{diversity} model, that favours labeling where superpixels have fewer number of unique labels. As an example from semantic segmentation, it is preferable to have pixels belonging to a superpixel to be incorrectly labeled with two class labels rather than three or more class labels. Let $\Gamma({\bf x_c})$ be the set of unique labels assigned to variables in the clique $c$, and $\omega_c$ be the weight associated with the clique. In our case, we take the clique potentials as proportional to the number of unique labels in the clique $c$:

\begin{equation}
  \phi_c({\bf x}_c) = \omega_c|\Gamma({\bf x_c})|
\label{eq:diversity_potential}
\end{equation}
where the notation $|A|$ denotes the cardinality of a set A.

@@

First, let us consider the IP formulation of the MAP problem for our diversity model. Using the same set of indicator variables $y_{ai} = \{0, 1\}$ as for the Potts model, which are binary now, the clique potential $\phi({\bf x_c})$ can be represented as

>>>>

We can augment the above pairwise models with higher-order potentials. Let $\mathcal C$ be the set of cliques, that is, fully-connected groups of variables. These cliques can, for instance, be the set of superpixels from an image segmentation method. Also, let ${\bf x}_c$ be the component of $\bf x$ formed by elements in clique $c$. The energy function now also contains higher-order potentials 
%
\begin{equation}
    E({\bf x}) = \sum_{a \in {\mathcal X}} \phi_a(x_a) + \sum_{(a, b) \in {\mathcal N}} \phi_{ab}(x_a, x_b) + \sum_{c \in {\mathcal C}} \phi_c({{\bf x}_c}),
    \label{eq:energy_hop_min}
  \end{equation}
%

@@

A higher-order model useful in real-world applications is the \textit{diversity} model, that favours labeling where superpixels have fewer number of unique labels. As an example from semantic segmentation, it is preferable to have pixels belonging to a superpixel to be incorrectly labeled with two class labels rather than three or more class labels. Let $\Gamma({\bf x}_c)$ be the set of unique labels assigned to variables in the clique $c$, and $\omega_c$ be the weight associated with the clique. In our case, we take the clique potentials as proportional to the number of unique labels in the clique $c$:

\begin{equation}
  \phi_c({\bf x}_c) = \omega_c|\Gamma({\bf x}_c)|
\label{eq:diversity_potential}
\end{equation}
where the notation $|A|$ denotes the cardinality of a set A.

@@

First, let us consider the IP formulation of the MAP problem for our diversity model. Using the same set of indicator variables $y_{ai} = \{0, 1\}$ as for the Potts model, which are binary now, the clique potential $\phi({\bf x}_c)$ can be represented as
